\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Chapter 1 Summary}
%\author{The Author}
\date{January 18, 2016}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

Shree Raj Shrestha

Write a one-page summary of Chapter One. Be sure to address the following:
\begin{itemize}
\item What were the activities of the Classical Age of Algebra?
\item Describe two modern algebras. How do they differ from classical algebra?
\item What algebraic structure did you study in Linear Algebra? What was the set? What were the operation?
\item What was Euclid's greatest feat and what does that have to do with Modern Algebra?
\item What is it that makes Modern Algebra abstract?
\item So...what is Abstract Algebra then?
\end{itemize}

Elementary algebra corresponds ot the classical age of algebra which spans from the sixteenth through the eighteenth centuries. In the classical age algebra was concerned with ways of solving equations. Some of the activities of the Classical Age of ALgebra was Cardan's discovery of the solution to the cubic equation, Tartaglia's discovery of solving cubic equation without the x term, Scipio's discovery fo solving cubic equations without the square term, Tartaglia's another discovery of solving any cubic equation, Ferrari's discovery of the general method for solving quartic equations, and Abel's discovery that there does not exist any formula (in the conventional sense) for the roots of algebraic equation whose degree is 5 or greater.

People, specifically mathematicians, of the Classical Age, according to the accounts presented, were involved in gambling, unhealthy competition, betrayl by loved ones, prosecution, massacres in cathedral, and keeping secrets to use in mathematical showdowns.

The two modern algebras are - Matrix algebra and boolean algebra. In its basic sense, modern algebra differed from classical algebra in that algebra was defined to be more than just "solving equations"; however, what more it entails depends on the abstraction set and the algebrac structure being used. There are almost 200 different kinds of algebraic systems in modern algebra arising from its connection with specific application or need.

The algebraic structure in Linear Algebra vector spaces and linear mappings between such spaces. The set in linear algebra is (linearly independent) vectors closed under row and column operations of matrices. To be more specific, matrix multiplication and matrix addition are some standard operation in Linear Algebra.

Euclid's greatest feat was his embodiment of the axiomatic method in its purest form in his book named "Elements" that contains 465 geometric propositions derived from deductive reasoning. This axiomatic method is a way of organizing, rather than discovering, facts. Euclid's pattern of organization was used by Descartes to organize human knowledge and Spinoza to create a deductive system of ethics.

Objects of mathematics are abstractions, idealizations of the properties of actual objects while retaining some properties like spatial relationships. Euclid's axiomatic method is important in modern algebra because it provides the basis for the notion of the algebraic structures, an abstration of concrete systems of algebra. Algebra today is organized axiomatically, hence making it abstract. Modern algebra, or the algebra today, is axiomatically organized where mathematicians study algbraic structures from a general point of view, compare, different structures and find relations between them.

Abstraction, in its basic sense, is the process of selecting what is relevant and disregarding everything else. Algebra, on the other hand, deals with algebraic structures represented by operations over a set. Hence, abstract algebra can be considered a form of algebra that involves operations over abstract sets. In a practical sense, these sets can range anything from numbers to set representing people or what they wear and any operations, changing clothes, meeting new people, etc can be considered an operation over the set (provided that operation is defined over the set).



Classical Age of Algebra
16th to 18th century



\end{document}  